### 2008-08-11 doc/glite_gateway/glite_gateway.tex
ldap query made more confortable
Installation guide extended

@@

@@

\verb#$ ldapsearch -x -h lxbra2305.cern.ch -p 2170 -b mds-vo-name=local,o=grid //#\\*
\verb#        '(GlueCEUniqueID=*cream*)'#

@@

\subsection{glitedelegate}
\label{glitedelegate}
If you want to submit a job to a gLite server, first you have to own a valid delegation on the remote site. You can either use an old, but still valid delegation identifier, or register a new one. There is a command line tool to register a delegation on the resource to be used.\par
The usage is very easy and straighforward. All you need is a working CREAM2 service URL, and a locally unique arbitrary delegation ID. This delegation ID will be associated to the remote resource. If you are not sure wether your favourite delegation ID is occupied or not, then try to delete it before registering it again. (See Section \ref{gliteundelegate} for further details!) The delegation command has the following syntax:
\begin{shaded}\verb#$ glitedelegate <delegation ID> <service URL>#\end{shaded}
For example:
\begin{shaded}\verb#$ glitedelegate test_delegation //#\\*
\verb#        https://cream.grid.upjs.sk:8443/ce-cream/services/gridsite-delegation#\end{shaded}
\subsection{glitesub}
\label{glitesub}
In the previous section it was shown how to create delegation. (See Section \ref{glitedelegate}!) This function, the job submission, is the only one which needs the delegation ID.\par The next step is to prepare the necessary input files and the job description!\par
The glitesub command syntax is the following:
\begin{shaded}\verb#$ glitesub -D <delegation ID> <service URL> <job description> <info file>#\end{shaded}
Here the delegation ID is the previously registered identification. The service URL will be different than in the delegation example above, because this is not the URL of the delegation, but the execution service. The job description must be in JDL format like in the example below. The info file stores information about job submitted. It should either be a non-existing file or it is overwritten. This file contains the job ID, the input sandbox URL, the output sandbox URL and the service URL. The submission command will take care of uploading the necessary input files up to the execution node.\par
It is important that the \textit{VirtualOrganisation} and \textit{QueueName} attributes should be the same as your virtual organisation name and the corresponding queue name on the server side.\par

@@

\begin{shaded}\verb#$ glitesub -D test_delegation //#\\*

@@

\begin{shaded}\verb#$ gliteundelegate test_delegation //#\\*

>>>>

\subsection{Generic installation disciplines}

@@

\subsection{Software installation on Debian Linux}
This section contains instructions how to install the software onto Debian Linux.
\begin{enumerate}
\item Put the Debian repository into the APT source files (/etc/apt/sources.list).
\begin{shaded}\verb#$ echo "deb http://pc02.inb.uni-luebeck.de:8080/~moeller/debian/stable ./" \#\\*
\verb#        >> /etc/apt/sources.list #\end{shaded}
\item Update the package list and install the necessary dependencies.
\begin{shaded}\verb#$ aptitude update#\\*
\verb#$ aptitude install voms globus globus-dev globus-doc#\end{shaded}
\item Configure the Globus libraries.
\begin{shaded}\verb#$ echo "/opt/globus/lib" > /etc/ld.so.conf.d/globus.conf#\\*
\verb#$ ldconfig#\end{shaded}
\item Install ARC1 client. There is a broken dependency that installs separately.
\begin{shaded}\verb#$ aptitude install nordugrid-arc1-client#\end{shaded}
\item Install Globus and VOMS specific files.
\begin{shaded}\verb#$ mkdir -p /opt/glite/etc/#\\*\end{shaded}
and copy these lines into the vomses file located /opt/glite/etc/vomses
\begin{footnotesize}
\verb#"gin.ggf.org" "kuiken.nikhef.nl" "15050" "/O=dutchgrid/O=hosts/OU=nikhef.nl/CN=kuiken.nikhef.nl" "gin.ggf.org"#\\*
\verb#"knowarc.eu" "arthur.hep.lu.se" "15001" "/O=Grid/O=NorduGrid/CN=host/arthur.hep.lu.se" "knowarc.eu"#\\*
\verb#"atlas" "voms.cern.ch" "15001" "/DC=ch/DC=cern/OU=computers/CN=voms.cern.ch" "atlas"#\\*
\verb#"nordugrid.org" "voms.uninett.no" "15015" "/O=Grid/O=NorduGrid/CN=host/voms.ndgf.org" "nordugrid.org"#\\*
\end{footnotesize}
\item Create \$HOME/.globus directory and move the user certificate-key pair into there.
\end{enumerate}

@@

\verb#$ ldapsearch -x -h lxbra2305.cern.ch -p 2170 -b mds-vo-name=local,o=grid \#\\*
\verb#        '(GlueCEUniqueID=*cream*)' | grep GlueCEInfoContactString | \#\\*
\verb#        awk '{print $2}' | sort | uniq#

@@

\subsection{glitedelegate}
\label{glitedelegate}
If you want to submit a job to a gLite server, first you have to own a valid delegation on the remote site. You can either use an old, but still valid delegation identifier, or register a new one. There is a command line tool to register a delegation on the resource to be used.\par
The usage is very easy and straighforward. All you need is a working CREAM2 service URL, and a locally unique arbitrary delegation ID. This delegation ID will be associated to the remote resource. If you are not sure wether your favourite delegation ID is occupied or not, then try to delete it before registering it again. (See Section \ref{gliteundelegate} for further details!) The delegation command has the following syntax:
\begin{shaded}\verb#$ glitedelegate <delegation ID> <service URL>#\end{shaded}
For example:
\begin{shaded}\verb#$ glitedelegate test_delegation \#\\*
\verb#        https://cream.grid.upjs.sk:8443/ce-cream/services/gridsite-delegation#\end{shaded}
\subsection{glitesub}
\label{glitesub}
In the previous section it was shown how to create delegation. (See Section \ref{glitedelegate}!) This function, the job submission, is the only one which needs the delegation ID.\par The next step is to prepare the necessary input files and the job description!\par
The glitesub command syntax is the following:
\begin{shaded}\verb#$ glitesub -D <delegation ID> <service URL> <job description> <info file>#\end{shaded}
Here the delegation ID is the previously registered identification. The service URL will be different than in the delegation example above, because this is not the URL of the delegation, but the execution service. The job description must be in JDL format like in the example below. The info file stores information about job submitted. It should either be a non-existing file or it is overwritten. This file contains the job ID, the input sandbox URL, the output sandbox URL and the service URL. The submission command will take care of uploading the necessary input files up to the execution node.\par
It is important that the \textit{VirtualOrganisation} and \textit{QueueName} attributes should be the same as your virtual organisation name and the corresponding queue name on the server side.\par

@@

\begin{shaded}\verb#$ glitesub -D test_delegation \#\\*

@@

\begin{shaded}\verb#$ gliteundelegate test_delegation \#\\*
